Hydras \& Co.

### 2022-03-11 doc/part-hydras.tex
minor corrections

\section{Ordinal Notations and \gaia's ordinals}
Module~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge} contains an instance of class \texttt{ON E0lt compare}, where \texttt{E0lt} is the order on the well-formed ordinal terms below $\epsilon_0$ defined in \gaia library (please see Chapter~\ref{gaia-chapter}).

@@

\subsection{About Gaia}
Chapter~\vref{gaia-chapter} describes the present state of a
project of making compatible the libraries \HydrasLib and \gaia. At present, both libraries contain a version of the inductive type \texttt{T1}, with the same base name for the constructors.

@@

@@

@@

>>>>

\section{Ordinal Notations and \gaia's ordinals}
\gaiasign Module~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge} contains an instance of class \texttt{ON E0lt compare}, where \texttt{E0lt} is the order on the well-formed ordinal terms below $\epsilon_0$ defined in \gaiaHydras library (please see Chapter~\ref{gaia-chapter}).

@@

\subsection{About Gaia}
\gaiasign Chapter~\vref{gaia-chapter} describes the present state of a
project of making compatible the libraries \HydrasLib and \gaia. At present, both libraries contain a version of the inductive type \texttt{T1}, with the same base name for the constructors.

@@

\emph{From Module~w}

@@

\paragraph*{\gaiasign}
 The library~\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} defines a \gaia-compatible type \texttt{E0}.

@@

    \paragraph*{\gaiasign}
    The module~\href{../theories/html/gaia_hydras.GHydra.html}{gaia\_hydras.GHydra} contains a proof of \gaiaHydras version of termination of all battles.

    \inputsnippets{GHydra/mDef, GHydra/mVariant, GHydra/Termination}
